\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-23 WOOT/Files/related_work.tex
update related-work

Under the premise of ensuring the full functionality of USB devices, there have been some works trying to improve the security during connection establishment.
Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices on the whitelist are allowed to communicate with the host. This prevents all potential attacks from untrusted devices. But this requires users to have a certain safety awareness and technical background to maintain a valid whitelist. For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution. There is a design can overcome this drawback. Mohammadmoradi et al\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically. This strategy first generates a unique fingerprint for each device based on its functionality. Then these fingerprints are used to maintain a safe and valid whitelist of USB devices. There is also work mediating USB connectivity for Industrial Control. TMSUI\cite{yang2015tmsui} relies on rich experience of administrator to build a whitelist. However, some modified USB devices may hide their real functionality from the user.

@@

After the USB enumeration and driver loading, there are also works trying to archive `defense in depth' against BadUSB attack.
Neuner et al.\cite{neuner2018usblock} prevents BadUSB attacks from malicious flash drive by analyzing the temporal characteristics of BadUSB-like attacks. This defense mechanism is effective because the attacker cannot obtain the screen of the host using just BadUSB. In this case, the malicious device can only inject key stoke in a very short time to reduce the risk of being discovered. This defect causes the typing characteristics of BadUSB to be detectable.  Pham et al. \cite{pham2010optimizing} block unsigned files from being Executed and automatically checks the driver signing option. What's more, in GoodUSB, a VM is deployed in host to as a honeypot to detect and stop malicious behavior of USB devices.

>>>>

Under the premise of ensuring the full functionality of USB devices, there have been some works trying to improve the security during connection establishment.
Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices on the whitelist are allowed to communicate with the host. This prevents all potential attacks from untrusted devices. But this requires users to have a certain safety awareness and technical background to maintain a valid whitelist. For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution. There are designs can overcome this drawback. For instance, Mohammadmoradi et al\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically. This strategy first generates a unique fingerprint for each device based on its functionality. Then these fingerprints are used to maintain a safe and valid whitelist of USB devices. There is another work mediating USB connectivity for Industrial Control. TMSUI\cite{yang2015tmsui} relies on rich experience of administrators to build a whitelist. However, some modified USB devices may hide their real functionality from the user.

@@

After the USB enumeration and driver loading, there are also works trying to archive `defense in depth' against BadUSB attack.
Neuner et al.\cite{neuner2018usblock} prevents BadUSB attacks from malicious flash drive by analyzing the temporal characteristics of BadUSB-like attacks. This defense mechanism is effective because the attacker cannot obtain the screen of the host using just BadUSB. In this case, the malicious device can only inject key stoke in a very short time to reduce the risk of being discovered. This defect causes the typing characteristics of BadUSB to be detectable.  Pham et al. \cite{pham2010optimizing} optimizing windows security features. It can block the execution of unsigned files, the installation of unsigned driver carried on portable media. What's more, in GoodUSB, a VM is deployed in host to as a honeypot to detect and stop malicious behavior of USB devices.
